Equilibria and Convergence of Fictitious Play on Network Aggregative Games

### 2021-05-27 Documents/FP in NAGs/neurips_2021.tex
various edits

\subsection{Contributions}

  The main contribution of this work is to introduce learning on the Network Aggregative Game
  through the action of Fictitious Play (FP).

@@

\subsection{Related Work}

\paragraph{Network Aggregative Games}

NA games are a recent introduction \cite{Parise2015} which presents
a variant of aggregative games by adding an underlying structure to
the population. Since its introduction, distributed algorithms have
been built with the aim of finding NE. In particular,
\cite{Parise2015, Parise2020} consider the case in which payoffs are
given by Lipschitz functions with unique minimisers and apply standard
topological fixed point towards designing algorithms which will
converge to the NE. Another approach for distributed NE seeking is the
projected gradient (resp. subgradient) dynamics which is explored in
\cite{Zhu2021} (resp. \cite{Shokri2020, Shokri2021}). In all of these
works, the cost function is assumed to be convex, and therefore have a
unique minimiser. In fact this is a common assumption in works
concerning NA Games \cite{Zhu2021, Lei2020}, which we believe is due
to its ubiquity in control settings. We have not yet come across works
which consider NA games from the point of view of payoff matrices,
which are more common in multi-agent learning settings.  Furthermore,
to the best of our knowledge, this is the first work which introduces
the application of a learning algorithm in the NA setting.

\paragraph{Fictitious Play}

Fictitious Play was introduced in 1951 \cite{Brown1949} as a 'natural'
way in which to approximate the Nash Equilibrium in zero sum games. Since then, a number of proofs of convergence have been determined for 2 player games \cite{Robinson1951, Miyasawa1961, Metrick1994,Berger2007, Monderer1997, Monderer1996}. However, the work looking
at FP where there are more than two agents is sparse. \cite{Sela1999}
considers a game in which a multi-player game is decomposed by
requiring that each agent engage in a two person game against each of
the opponent. Their payoff is given by the sum of payoffs in all of
these subgames. It was found that, if this game is zero sum, then FP
will converge. Similar results for more than two players were found
for games where all agents share the same payoff in
\cite{Monderer1996}. In \cite{Perrin2020}, the action of FP was
considered in a Mean Field Game, with convergence in zero sum
games. The most general result, and the one most similar to our own,
was found by Ewerhart and Valkanova in 2020 \cite{Ewerhart2020}. It was found that FP converges in network games, where each
agent is engaged in a two-player game with each of their neighbours
Our work adapts this model to consider NA Games, so that the agents do not play
individual games against each of their neighbours but rather a single
game against the aggregate of their neighbours. We also
extend a result for two player games found by Ostrovski and van Strien
\cite{Ostrovski2014} which showed that FP achieves no-regret to the
multi-player setting.

@@

\section{Convergence of Fictitious Play}
\label{sec::CTFPAnalysis}

@@

\section{NA-CTFP achieves no regret}
  \label{sec::CCEConvergence}

  In this section we aim to understand the long term behaviour of NA-CTFP for the
  case in which NA games are not necessarily zero-sum. To do this, we first introduce the coarse correlated equilibria (CCE) \cite{Nisan2007} in the context of NA games as a natural extension to the two-player case. Then, we show that the NA-CTFP process converges to the set of
  CCE
  %
  \begin{definition}[CCE] \label{def::CCE}
    A distribution $\mathcal{D}$ over the joint action set $S =
    \times_\mu S^\mu$ is called a \emph{coarse correlated equilibrium}
     if, for all agents $\mu$, $
      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
      \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (j, s^{-
          \mu})]$ $ \forall j \in S^\mu.$
  \end{definition}

@@

  For an NA game, a set of actions $s = (s^1, \ldots, s^N)$ which is
  drawn from a joint probability distribution $\mathcal{D}$, also generates
  a corresponding set of reference vectors $\sigma =
  (\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in
    N^\mu} \wmunu s^\nu$. In other words, if we draw $s$ from $\mathcal{D}$, then we have also drawn $\sigma$, which means our CCE condition, Def.~\ref{def::CCE}, can be written as $
\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, \refmu)] \geq
\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (j, \refmu)]$ $ \forall j \in S^\mu$ and all agents $\mu$.

@@

    in which $\pure{\mu}{i}$ denotes the probability vector in $\Delta_\mu$ with $1$ in the slot
    $i'$ and $0$ everywhere else. Note, this is the \emph{average regret} for the agent $\mu$
    and, of course, can be related to the \emph{cumulative regret} which is used for analysis
    in \cite{Leonardos2020, Cesa-Bianchi2021}.  To illustrate the average regret, let us
    consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$
    is given by
%    
    \begin{equation*}
      u^{\mu}(x^\mu(t), \sigma(t)) = \sum_{ij} a_{ij} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{21} x_2^\mu \sigma_1^\mu + a_{22} x_2^\mu \sigma_2^\mu
    \end{equation*}

@@

    \begin{equation*}
      u^{\mu}(\pure{\mu}{1}, \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu 
    \end{equation*}

    By comparing the two expanded expressions, we can see that the latter gives the reward that agent $\mu$ would have received had they played action $1$ throughout the entire play, assuming that the behaviour of the other agents (encoded in $\sigma$) does not change. As such, this is a measure of agent $\mu$'s regret, in hindsight, for not playing action $1$ the entire time. An agent achieves \emph{no regret} if $R^\mu$ is non-positive.
  \end{remark}

@@

\section{Numerical Experiments}

  \subsection{Non-convergent examples} \label{sec::NonConv}

>>>>

\paragraph{Contributions.}
%
  The main contribution of this work is to introduce learning on the Network Aggregative Game
  through the action of Fictitious Play (FP).

@@

\paragraph{Related Work.}

\textbf{Network Aggregative Games}
%NA games
are a recent introduction \cite{Parise2015} which presents
a variant of aggregative games by adding an underlying structure to
the population. Since its introduction, distributed algorithms have
been built with the aim of finding NE. In particular,
\cite{Parise2015, Parise2020} consider the case in which payoffs are
given by Lipschitz functions with unique minimisers and apply standard
topological fixed point towards designing algorithms which will
converge to the NE. Another approach for distributed NE seeking is the
projected gradient (resp. subgradient) dynamics which is explored in
\cite{Zhu2021} (resp. \cite{Shokri2020, Shokri2021}). In all of these
works, the cost function is assumed to be convex, and therefore have a
unique minimiser. In fact this is a common assumption in works
concerning NA Games \cite{Zhu2021, Lei2020}, which we believe is due
to its ubiquity in control settings. We have not yet come across works
which consider NA games from the point of view of payoff matrices,
which are more common in multi-agent learning settings.  Furthermore,
to the best of our knowledge, this is the first work which introduces
the application of a learning algorithm in the NA setting.

\textbf{Fictitious Play}
%Fictitious Play
was introduced in 1951 \cite{Brown1949} as a 'natural'
way in which to approximate the Nash Equilibrium in zero sum games. Since then, a number of proofs of convergence have been determined for 2 player games \cite{Robinson1951, Miyasawa1961, Metrick1994,Berger2007, Monderer1997, Monderer1996}. However, the work looking
at FP where there are more than two agents is sparse. \cite{Sela1999}
considers a game in which a multi-player game is decomposed by
requiring that each agent engage in a two person game against each of
the opponent. Their payoff is given by the sum of payoffs in all of
these subgames. It was found that, if this game is zero sum, then FP
will converge. Similar results for more than two players were found
for games where all agents share the same payoff in
\cite{Monderer1996}. In \cite{Perrin2020}, the action of FP was
considered in a Mean Field Game, with convergence in zero sum
games. The most general result, and the one most similar to our own,
was found by Ewerhart and Valkanova in 2020 \cite{Ewerhart2020}. It was found that FP converges in network games, where each
agent is engaged in a two-player game with each of their neighbours
Our work adapts this model to consider NA Games, so that the agents do not play
individual games against each of their neighbours but rather a single
game against the aggregate of their neighbours. We also
extend a result for two player games found by Ostrovski and van Strien
\cite{Ostrovski2014} which showed that FP achieves no-regret to the
multi-player setting.

@@

\section{Convergence of Fictitious Play  in Network Aggregative Games}
\label{sec::CTFPAnalysis}

@@

\section{Fictitious Play  in Network Aggregative Games Achieves No Regret}
  \label{sec::CCEConvergence}

  In this section we aim to understand the long term behaviour of
  NA-CTFP for the case in which NA games are not necessarily
  zero-sum. To do this, we first introduce the coarse correlated
  equilibria (CCE) \cite{Nisan2007} in the context of NA games as a
  natural extension to \fb{of} the two-player case. Then, we show that
  the NA-CTFP process converges to the set of CCE.
  %
  \begin{definition}[CCE] \label{def::CCE}
    A distribution $\mathcal{D}$ over the set $S = \times_\mu S^\mu$
    of joint actions is called a \emph{coarse correlated equilibrium}
    if, for all agents $\mu$ and actions $j \in S^\mu$, we have
    $\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq
    \mathbb{E}_{s \sim \mathcal{D}}[u^\mu (j, s^{- \mu})]$.
  \end{definition}

@@

  For an NA game, a set of actions $s = (s^1, \ldots, s^N)$ which is
  drawn from a joint probability distribution $\mathcal{D}$, also
  generates a corresponding set of reference vectors $\sigma =
  (\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in
    N^\mu} \wmunu s^\nu$. That is, if we draw action $s$ from
  $\mathcal{D}$, then we have also drawn $\sigma$, which means our CCE
  condition, Def.~\ref{def::CCE}, can be written as $ \mathbb{E}_{s
    \sim \mathcal{D}}[u^\mu (s^\mu, \refmu)] \geq \mathbb{E}_{s \sim
    \mathcal{D}}[u^\mu (j, \refmu)]$, for all agents $\mu$ and actions $j \in S^\mu$.

@@

    in which $\pure{\mu}{i}$ denotes the probability vector in $\Delta_\mu$ with $1$ in the slot
    $i'$ and $0$ everywhere else. Note, this is the \emph{average regret} for the agent $\mu$
    and, of course, can be related to the \emph{cumulative regret} which is used for analysis
    in \cite{Leonardos2020, Cesa-Bianchi2021}.  To illustrate the average regret, let us
    consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$
    is given by
%    
    \begin{equation} \label{eq1}
      u^{\mu}(x^\mu(t), \sigma(t)) = \sum_{ij} a_{ij} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{21} x_2^\mu \sigma_1^\mu + a_{22} x_2^\mu \sigma_2^\mu
    \end{equation}

@@

    \begin{equation}  \label{eq2}
      u^{\mu}(\pure{\mu}{1}, \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu 
    \end{equation}

    By comparing equations~(\ref{eq1}) and (\ref{eq2}),
    %the two expanded expressions,
    we can see that the latter gives the reward that agent $\mu$ would have received had they played action $1$ throughout the entire play, assuming that the behaviour of the other agents (encoded in $\sigma$) does not change. As such, this is a measure of agent $\mu$'s regret, in hindsight, for not playing action $1$ the entire time. An agent achieves \emph{no regret} if $R^\mu$ is non-positive.
  \end{remark}

@@

\section{Experimental Evaluation}

  \subsection{Non-convergence of General Two-player Games under NA-CTFP} \label{sec::NonConv}
